Robustly decorrelating errors with mixed quantum gates

### 2020-04-11 decorrelation/mixed_unitaries.tex
adding ptm

\subsection{Experimental implementation } % (fold)
\label{sub:experimental}
\noindent We implemented our methods using the 19Q-Acorn superconducting transmon processor at Rigetti Computing. Comprehensive characterization of this device can be found in \cite{1712.05771}. While this device consisted of 20 qubits with fixed couplings, we used only qubit \#8 for our demonstration. Controls were derived from a single, 10-sample, 50ns Gaussian $X_{\pi/2}$ pulse calibrated via Rabi oscillation. Four intentionally miscalibrated Gaussian pulses, labeled $\mathsf{Pulse1}$ through $\mathsf{Pulse4}$, were derived by scaling the amplitude of the calibrated $X_{\pi/2}$ pulse by a factor $S \in \{1.064, 1.039,0.937, 0.912\}$, respectively. We model their effect on the qubit state as perfectly unitary rotations, $X_{A \pi/2} = \exp{(-i A \pi/2 \sigma_x)}$. These gates are then used as in Sec.~\ref{sub:off_diagonals} to construct a Pauli-exact MQG, which samples from the miscalibrated waveforms with probabilities $P\in \{0.307, 0.283, 0.211, 0.199\}$ respectively. Using these probabilities and pulse amplitudes we have plotted the corresponding Pauli transfer matrices in Fig. \ref{ptms}. $\mathsf{Pulse1}$ through $\mathsf{Pulse4}$ show clear coherent errors as off-diagonal elements while the MQG exhibits a clear supression of these off-diagonal elements.
\begin{figure}
\includegraphics[scale=.5]{experimental-ptm.png}
\label{ptms}
\caption{Pauli transfer matrices for a) $\mathsf{Pulse1}$, b) $\mathsf{Pulse2}$, c) $\mathsf{Pulse3}$, d) $\mathsf{Pulse4}$ and e)a Pauli-exact MQG. The four constituent pulses can be seen to have coherent error from the off-diagonal components of their Pauli transfer matrices, while the Pauli-exact MQG has been constructed to have minimal coherent error and therefore has predominantly diagonal elements.}   
\end{figure}

>>>>

\subsection{Experimental implementation } % (fold)
\label{sub:experimental}
\noindent We implemented our methods using the 19Q-Acorn superconducting transmon processor at Rigetti Computing. Comprehensive characterization of this device can be found in \cite{1712.05771}. While this device consisted of 20 qubits with fixed couplings, we used only qubit \#8 for our demonstration. Controls were derived from a single, 10-sample, 50ns Gaussian $X_{\pi/2}$ pulse calibrated via Rabi oscillation. Four intentionally miscalibrated Gaussian pulses, labeled $\mathsf{Pulse1}$ through $\mathsf{Pulse4}$, were derived by scaling the amplitude of the calibrated $X_{\pi/2}$ pulse by a factor $S \in \{1.064, 1.039,0.937, 0.912\}$, respectively. We model their effect on the qubit state as perfectly unitary rotations, $X_{A \pi/2} = \exp{(-i A \pi/2 \sigma_x)}$. These gates are then used as in Sec.~\ref{sub:off_diagonals} to construct a Pauli-exact MQG, which samples from the miscalibrated waveforms with probabilities $P\in \{0.307, 0.283, 0.211, 0.199\}$ respectively. Using these probabilities and pulse amplitudes we have plotted the corresponding Pauli transfer matrices, minus the identity, in Fig. \ref{ptms}. We have removed the identity from the plot to highlight the small diagonal elements of the MQG $\mathsf{Pulse1}$ through $\mathsf{Pulse4}$ show clear coherent errors as off-diagonal elements while the MQG exhibits a clear supression of these off-diagonal elements.
\begin{figure}
\includegraphics[scale=.5]{experimental-ptm.png}
\label{ptms}
\caption{Pauli transfer matrices with the identity subtracted off for the error maps of a) $\mathsf{Pulse1}$, b) $\mathsf{Pulse2}$, c) $\mathsf{Pulse3}$, d) $\mathsf{Pulse4}$ and e)a Pauli-exact MQG. The four constituent pulses can be seen to have coherent error from the off-diagonal components of their Pauli transfer matrices. The Pauli-exact MQG has been constructed to have minimal coherent error and therefore only has diagonal elements. }   
\end{figure}
